---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# KMeans

<!-- badges: start -->
[![License: GPL v3](https://img.shields.io/badge/License-GPLv3-blue.svg)](https://www.gnu.org/licenses/gpl-3.0) ![GitHub repo size](https://img.shields.io/github/repo-size/Prapti-044/Kmeans) ![GitHub code size in bytes](https://img.shields.io/github/languages/code-size/Prapti-044/Kmeans) ![GitHub language count](https://img.shields.io/github/languages/count/Prapti-044/Kmeans) ![GitHub top language](https://img.shields.io/github/languages/top/Prapti-044/Kmeans)
<!-- badges: end -->

The goal of KMeans is to learn how to create an R-package by implementing [KMeans clustering agorithm](https://en.wikipedia.org/wiki/K-means_clustering) for clustering a dataset.

_Note_: This RMarkdown is created following the guidelines of [this R-package example](https://github.com/mvuorre/exampleRPackage).

## Installation

You can only install the development version from [this repository](https://github.com/Prapti-044/KMeans) with:

``` r
# install.packages("devtools")
devtools::install_github("Prapti-044/KMeans")
```
## Example

This is a basic example which shows you how to cluster the iris dataset:

```{r example}
library(KMeans)
result <- apply.kmeans(iris[,-5], 3, 300)
str(result)
```
